\documentclass[times, 11pt]{AeroResearchProposal}

% Put header info here:  Short title and author name
\fancyHeader{Short Title}{Author Name}

% university
\university{Technion - Israel Institute of Technology}

% facutly
\department{Department of Aerospace Engineering}

% research proposal
\subject{Research Proposal: Master of Science in AE/ Master of Science}

% title in English and Hebrew
\thesisTitleEN{Thesis Title\\\texthebrew{שם המחקר בעברית }}

% student name, email, and student number
\authorOne{First Last}{studentEmail@technion.ac.il}{ID: 123456789}


% supervisors
\supervisors{Supervisor Name}{University, Faculty, Location}

\theDate{\today} 

\begin{document}
\titlePage

\mainmatter
% ===== Content: Modify the structure according to your needs =======
\noindent\fbox{%
    \parbox{\textwidth}{%
        This is the suggested template for MSc research proposals for study within the Faculty of Aerospace Engineering at the Technion.  Templates are available for \LaTeX and MSWord. The following format guidelines should be strictly adhered to:
        \begin{enumerate}\itemsep0em
            \item The research proposal shall not exceed 2 pages.  The page count does not include the title page and the references.
            \item Use an 11pt font size, 1.5 line spacing, and 2cm page margins.
            \item Proposals must be submitted as a PDF document.
        \end{enumerate}
    }%
}

\section*{Introduction}

\alert{The introduction should provide a high-level motivation and description of the problem you wish to solve.  It should include a literature review together with a clear identification of open problems in the research area} \cite{Berndtsson607210}.


\section*{Problem Statement}

\alert{Provide a brief description of what problem you are going to investigate in your thesis work. Provide 2 to 4 clear and concrete problems that will be the core of the thesis work.}


\section*{Methodology}
\alert{Describe the steps you will take in attempting to answer your research question or whether you will follow a known scientific or engineering method.}


\section*{Research Plan and Timeline}
\alert{Describe the activities that must be performed during the work, in which order and how long to you plan to have them. It is not enough to copy-paste the important dates for the course.}

\bibliographystyle{IEEEtran}
\bibliography{references}

\bigskip
\warning{[REMOVE ALL THE INSTRUCTIONS MARKED WITH RED COLOR BEFORE SUBMITTING YOUR PROPOSAL.]}


\end{document}
